Data Management \\ and LSST Special Programs

### 2022-02-21 ap_docrev.tex
fix typo

In Section 2.4.1.1.2, ``Non-Standard Visit", LSR-REQ-0111\req{0111} requires that the LSST system {\it ``be capable of obtaining and processing exposures not taken in a standard visit mode including those with a minimum exposure time of"} 1 second ({\tt minExpTime}\reqparam{minExpTime}).
The discussion notes that {\it ``non-standard visit exposures may possibly be degraded in some aspects of performance (e.g. cosmic ray rejection on visits consisting of a single exposure), and might be incompatible with difference imaging and alert production (e.g., short exposures in which the PSF is
not fully formed)"}.

@@

In Section 3.6.3.5, ``Offset Pointing", OSS-REQ-0302\ossreq{0302} specifies that {\it ``the LSST shall be capable of offset pointing within a single field-of-view with a precision of no more than" 0.2 arcseconds ({\tt offsetPointingErr}\reqparam{offsetPointingErr}).

>>>>

In Section 2.4.1.1.2, ``Non-Standard Visit", LSR-REQ-0111\lsrreq{0111} requires that the LSST system {\it ``be capable of obtaining and processing exposures not taken in a standard visit mode including those with a minimum exposure time of"} 1 second ({\tt minExpTime}\reqparam{minExpTime}).
The discussion notes that {\it ``non-standard visit exposures may possibly be degraded in some aspects of performance (e.g. cosmic ray rejection on visits consisting of a single exposure), and might be incompatible with difference imaging and alert production (e.g., short exposures in which the PSF is
not fully formed)"}.

@@

In Section 3.6.3.5, ``Offset Pointing", OSS-REQ-0302\ossreq{0302} specifies that {\it ``the LSST shall be capable of offset pointing within a single field-of-view with a precision of no more than"} 0.2 arcseconds ({\tt offsetPointingErr}\reqparam{offsetPointingErr}).
